Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Including WHY did we chose these tools

Many tools for companies, as well as for devices, have adopted the BYOD have been released in the past four years. This way, and
more focused on the enterprise, there are some tools which offer the CSO ways to control the devices which enter into the system, for instance, and also to protect the employees' data by means of data encryption and data protection by requiring the use of strong and secure passwords. Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs, like Good's BYOD solution (see Section \ref{subsec:othertools}). On the other hand, many solutions have been presented which are more focused on the device side, although they implement also the server side. This is the case, for instance, of Android for Work (see Section \ref{subsec:androidwork}). Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}), which can complement them, as adds other features that go beyond the state of the art. This section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.

>>>>

Many tools for companies, as well as for devices, have adopted the BYOD have been released in the past four years. This way, and
more focused on the enterprise, there are some tools which offer the CSO ways to control the devices which enter into the system, for instance, and also to protect the employees' data by means of data encryption and data protection by requiring the use of strong and secure passwords. Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs, like Good's BYOD solution (see Section \ref{subsec:othertools}). On the other hand, many solutions have been presented which are more focused on the device side, although they implement also the server side. This is the case, for instance, of Android for Work (see Section \ref{subsec:androidwork}). Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}), which can complement them, as adds other features that go beyond the state of the art. The products that have been reviewed were chosen either because they have appeared in top-10 web articles \footnote{\url{http://www.networkworld.com/article/2357899/data-center/108866-10-Mobile-Device-Management-Leaders-That-Help-IT-Control-BYOD.html#slide11}}, or they have been developed for the main smartphone platforms \footnote{\url{http://www.idc.com/prodserv/smartphone-os-market-share.jsp}}. Actually, the selection process have been diffiicult, as some of the initially found tools or companies in the web were bought by others that we do review here. Also, because this market is still growing, there are not many solutions to review, and here we display the ones more alike to MUSES. This section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.
